Accessing the nucleon transverse structure in inclusive deep inelastic scattering

### 2017-07-26 1607 - JMC for g2/Paper/Reply_to_Referee.txt

We thank the reviewer for the thoughtful comments and questions about our work, that we have carefully considered and incorporated in the revised version of our paper. In the following, we comment upon each point raised by the reviewer, and refer to the appropriate place in the text where major changes have occurred. (As the numbering of the equations has changed slightly in the revision, in our answers we refer to the new numbering.) We are confident the new version wil satsify the Referee, but will be glad to make further improvements should teh discusssions need to be clarified further.

> 1. The new term, the last term in Eq. (21), has the non-perturbative
> mass scale M_q and the (perturbative) current quark mass m_q come in
> on the same footing. Have the authors tried to verify their
> conclusions in an explicit calculation? For instance, perhaps
> calculating the correlator \Xi from (4) in some non-perturbative model
> may help illustrate the fact that M_q - m_q is in fact non-zero.

We have indeed checked the behavior of the Mq term in a model with a pseudoscalar Yukawa interaction modeling the uark fragmentation process. This clearly show that Mq>mq. We added a comment to this effect at the end of Section II together with a revised discussion of the estimate of the magnitude of Mq, see next.

> 2. If I understood the arguments above Eq. (9) correctly,
> strictly-speaking the conclusion there is that M_q < O (100 MeV), not
> equal to O (100 MeV) as Eq. (9) has. In fact, {\bar J}_2 can be very
> small as far as one can tell, leading to M_q = m_q. Some
> clarifications would help here.

The Referee is right in noticing that nothing a pripori prevents Mq to become smaller than ~100 MeV. Our estimate was based on the fact that one can expect the two-particle continuum to open up at (mq+m_pi)~m_pi~Lambda_QCD, and therefore the value of mu averaged over the J2 distribution should be around our originally quoted value. We have revised this estimate taking also into acocunt that a quark is in fact not a physical asymptotic state, and Mq could be smaller than that, and now quotw Mq~10-100 MeV.

Note that, having exactly Mq=mq would imply the existence of a so far unknown symmetry or otherwise general constraint that would be extremely interesting on its own. Although we judge this unlikely, our paper may, if nothing else, encourage people to prove us wrong and discover a new feature of QCD.

The modified discussion, incorporating alsocomment #1, can be found at the end of Section II.

> 3. The sum rule (31) raises the question of whether the integral on
> its right-hand side is finite. It is hard for me to imagine a
> realistic scenario in which it is. In perturbation theory unpolarized
> TMDs at small x scale as (1/x)^{1+\epsilon_1}, where \epsilon_1 is an
> order-\alpha_s positive perturbative correction, while 1 in the power
> is ultimately determined by the gluon spin =1. Some polarized TMDs,
> such as helicity, scale as (1/x)^{\epsilon_2} at small x with
> \epsilon_2 an order-\sqrt{\alpha_s} positive perturbative correction,
> as found e.g. in Ref. [41]. Note that neither of those behaviors gives
> a finite right-hand side of (31). The scenario considered by the
> authors in Eq. (32) corresponds to negative \epsilon_2: while I know
> of no theorem requiring \epsilon_2 > 0, I also know of no perturbative
> calculation where \epsilon_2 < 0 either. (Furthermore, in N=4 SYM
> theory, where the unpolarized intercept is known to a very high order
> in perturbation theory, the series in \alpha_s changes sign only every
> other term, see Eq. (5.1) in 1504.06640.) Saturation effects at very
> low x can at most effectively put \epsilon_2 =0, still not making the
> right-hand side of (31) finite... So, as a friendly colleague I urge
> the authors to rethink their conclusions very carefully.

We agree with the referee, and in fact our original discussion was somewhat confusing. We have enlarged teh scope of the discussion and reviewed some perturbative and resummed results on the small x behavior of h1. The small-x physics of the h1 function in comparison to g1 is indeed an interesting topic of research, that can now also be accessed experimentally thanks to our extended WW and BC relations.

The modified discussion can be found in teh paragraph above Eq.()

> 4. Here are some minor corrections:
>
> -- Ref. [22] has 3 authors, but only two are mentioned explicitly in
>    the text three lines above Eq. (1).
>
> -- The kinematics of the diagrams in Fig. 1 is not defined: e.g., is
>    the proton moving in the light-cone "+" or "-" direction? This is
>    needed to better understand the discussion between Eqs. (6) and
>    (7).
>
> -- The equation in the text two lines above Eq. (9) should have m_q^2
>    (instead of m_q) inside the delta-function.

We thank the referee also for this level of attention to our work, that has indeed helped us to improve the article.

### 2017-07-26 1607 - JMC for g2/Paper/JMC_dis.tex
Reply to referee v1.1

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering
off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons --  a process that can be described in terms of suitable ``jet'' correlators. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
non perturbatively and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, putting constraints on the small-$x$ behavior of the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
\end{abstract}

@@

The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a non perturbative mass of order 100 MeV, much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes. Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
contribution already in one-photon exchange processes, and more precisely to the inclusive $g_2$ structure function. The new term is proportional to the transversity distribution function multiplied by a new nonperturbative ``jet mass'', which will be precisely defined below, and has the interesting features that:
(a) it violates the Wandzura--Wilczek relation;
(b) it extends the Burkhardt--Cottingham sum rule, providing a useful bound on the small-$x$ behavior of the transversity distribution;
(c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
We estimate this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.

@@

Motivated by mass corrections to inclusive DIS structure functions at large values of the Bjorken invariant $x_B$,
Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
a ``jet correlator'', also called ``jet factor'' by Collins and Rogers in Ref.~\cite{Collins:2007ph}, that accounts for invariant mass production in the current region and ensures that leading twist calculations in collinear factorization are consistent with the $x_B<1$ requirement imposed by baryon number conservation. \cite{Accardi:2008ne}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align}
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark's four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, the correlator's gauge invariance is explicitly guaranteed the two Wilson line operators ${\cal
  U}^{n_+}$, that run to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details. This path choice for the Wilson line is required by QCD factorization theorems, and the vector $n_+$ is determined by the particular hard process to which the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

@@

\begin{figure*}[bt]
  \centering
  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
  \hfill
  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
  \hfill
  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
  \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part. Note the gluon attaches to both the nucleon and jet correlators. The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
  }
  \label{fig:handbags}
\end{figure*}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order ${\cal O}(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}. In this paper, where we limit our
attention to effects of order ${\cal O}(1/Q)$, we can neglect $k^-$ compared to $q^-$. As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
    +  \xi_2 \frac{\nslash_-}{2} 
    + {\cal O}(l_T/l^-) + \text{higher\ twists} \ .
\end{equation} 
The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to ${\cal O}(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
\end{align} 
where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.
It is important to notice that while $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass $0 < \mj < \int d\mu^2 \mu J_2(\mu^2)$ is dynamically determined. From the analytic properties of the spectral functions we know that $J_2(\mu^2) = Z \delta(\mu^2-m_q) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$ with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects. Taking into account that $J_1 < J_2$, we may therefore estimate 
\begin{align}
  \label{eq:mjet}
  \mj = {\cal O}(100 \text{\ MeV}) \ .
\end{align}
Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that on the perturbative vacuum, 
\begin{align*}
  \Xi^\text{pert}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
\end{align*}
where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
However, we are here considering non perturbative effects
in the quark propagation, and $\mj \gg \mq$. 
Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

@@

One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule is still satisfied at least
asymptotically.
At finite scales, however, the only way to preserve the validity of the
BC sum rule is if
$
%\begin{align}
   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
\label{eq:ABsumrule}
%\end{align}
$
Interestingly, one can show that this constraint, if valid at any given scale
$Q_0$ is conserved through QCD evolution. However, we think that it is unlikely to be satisfied in general, since it is explicitly broken in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}. Then, if we assume that the BC sum rule is broken by a {\em finite} amount we obtain that $h_1(x)/x$ must be integrable, which implies the following bound on the small $x$ behavior of the transversity: 
\begin{align}
  h_1^q(x) \propto x^\epsilon \ \ \ \epsilon>0 \ .
\label{eq:ABbound}
\end{align}
This bound can be very useful, \eg, in transversity fits, where the data at
small $x$ is, as yet, very limited, and in general for proper extrapolations
to $x_B=0$ when experimentally measuring moments. We also note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently investigated in Ref.~\cite{Kovchegov:2016zex}; it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$.

@@

For both the $d_1$ and $d_2$ moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
or fitted \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa}.
Furthermore, the bound
\eqref{eq:ABbound} promises to improve future transversity fits. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.

We should also note that the $\mj$ jet mass parameter can
also be experimentally measured, \eg, in electron-positron collisions.
A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.\ref{fig:epl_emn_h}.
In single-hadron production, the fragmentation functions 
play the role of PDFs in DIS and couple to the jet functions
in an analogous way. To access the spin-flip $J_1$ function one needs to detect a polarized hadron, such as a $\Delta$ baryon. 
In double hadron production, the enlarged number of Dirac structures
of the dihadron fragmentation correlators related to the relative momentum of the two hadrons \cite{Bacchetta:2002ux,Bacchetta:2003vn} allows one to access
the jet function in novel ways, and in particular to isolate the
contribution from the helicity-flip $J_1$ term in combination with the
chiral-odd fragmentation function $H_1^{\sphericalangle}$.

@@

In this paper, we revisited the inclusive DIS analysis, including the
effects due to the production of a system of final state hadrons in the current direction, which we
conveniently referred to as a ``jet.'' We described this in terms of a jet
correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function, and of a quark-gluon-quark jet correlator needed to insure gauge invariance of the calculation.
We then carried out the analysis of
the DIS cross section up to contribution of order $1/Q$. 
The introduction of the jet correlators 
leads to a difference in the expression of the structure function $g_2$ in
inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(100 MeV)
and to the transversity distribution function. This new term
contributes to the violation of the Wandzura-Wilczek relation, in addition to
the standard pure twist-3 terms and quark mass corrections. Contrary to these
standard terms, however, the new jet mass correction does not necessarily integrate to zero and so violates also the
Burkhardt--Cottingham and Efremov--Teryaev--Leader sum rules. This is yet another example of how surprising
and rich the phenomenology of polarized inclusive DIS can be.

>>>>

\begin{abstract}
We revisit the standard analysis of inclusive Deep Inelastic Scattering
off nucleons taking into  account the fact that on-shell quarks cannot be present in the final state, but they rather decay into hadrons --  a process that can be described in terms of suitable ``jet'' correlators. As a consequence, a spin-flip term
associated with the invariant mass of the produced hadrons is generated
nonperturbatively and couples to the target's transversity distribution
function. In inclusive cross sections, this provides an hitherto neglected and
large contribution to the twist-3 part of the $g_2$ structure function, that
can explain the discrepancy between recent calculations and fits of this
quantity.  It also provides an extension of the Burkhardt--Cottingham sum rule, 
providing new information on the transversity function, as well as an extension of the Efremov--Teryaev--Leader sum rule, suggesting a novel way to measure the tensor charge of the proton.
\end{abstract}

@@

The jet correlators describe interactions of a perturbative quark with vacuum fields, that break chiral symmetry and generate a nonperturbative mass
estimated in the 10-100 MeV range, potentially
much larger than the current quark mass for light flavors, as also heuristically advocated in Ref.~\cite{Afanasev:2007ii} for a study of transverse target single-spin asymmetries in two-photon exchange processes. Here, we formalize this idea in the context of collinear factorization, and observe that jet correlators introduce a new
contribution already in one-photon exchange processes, and more precisely to the inclusive $g_2$ structure function. The new term is proportional to the transversity distribution function multiplied by a new nonperturbative ``jet mass'', which will be precisely defined below, and has the interesting features that:
(a) it violates the Wandzura--Wilczek relation;
(b) it extends the Burkhardt--Cottingham sum rule, providing new useful information on behavior of the transversity distribution;
(c) it also extends the Efremov--Teryaev--Leader sum rule, providing a novel way to measure the proton's tensor charge.
We estimate this new jet-mass-induced contribution based on a recent extraction of the transversity distribution, and show it can indeed be very large.

@@

Motivated by mass corrections to inclusive DIS structure functions at large values of the Bjorken invariant $x_B$,
Accardi and Qiu \cite{Accardi:2008ne} have introduced in the LO handbag diagram 
a ``jet correlator'', also called ``jet factor'' by Collins, Rogers, and Stasto in Ref.~\cite{Collins:2007ph}, that accounts for invariant mass production in the current region and ensures that leading twist calculations in collinear factorization are consistent with the $x_B<1$ requirement imposed by baryon number conservation. \cite{Accardi:2008ne}. The jet correlator is depicted in
Figure~\ref{fig:handbags}(a) and is defined as 
\begin{align}
\Xi_{ij}(l,n_+) =\int
  \frac{\de^4\eta}{(2\pi)^4}\; e^{i l \cdot \eta}\,
    \langle 0|\, {\cal U}^{n_+}_{(+\infty,\eta)}
\,\psi_i(\eta)
             \bar{\psi}_j(0)\,
{\cal U}^{n_+}_{(0,+\infty)}\,   |0 \rangle \ ,
\label{e:xifull}
\end{align} 
In this definition, $l$ is the quark's four-momentum, $\Psi$ the quark field
operator (with quark flavor index omitted for simplicity), and $|0\rangle$ is
the nonperturbative vacuum state. Furthermore, the correlator's gauge invariance is explicitly guaranteed the two Wilson line operators ${\cal
  U}^{n_+}$, that run to infinity first along along a light-cone plus direction determined by the vector $n_+$, then along the direction transverse to that vector, see \cite{Bacchetta:2006tn} for details. This path choice for the Wilson line is required by QCD factorization theorems, and the vector $n_+$ is determined by the particular hard process to which the jet correlator contributes. For example, in the case of inclusive DIS
discussed in this paper, this is determined by the four momentum transfer $q$
and the proton's momentum $p$.

@@

\begin{figure*}[bt]
  \centering
  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
  \hfill
  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
  \hfill
  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
  \caption{Diagrams contributing to inclusive DIS scattering up to twist-3, including a jet correlator in the top part. The proton is moving dominantly in the light-cone plus direction, and the jet in the minus direction. In diagrams (b) and (c), the gluon attaches to both the nucleon and jet correlators. The Hermitian conjugates of these two diagrams, i.e., with gluons attaching to the right of the cut, are not shown.
  }
  \label{fig:handbags}
\end{figure*}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the integration over $dl^+$, or equivalently $dl^2/(2l^-)$, is kinematically coupled to the other integrations, and induces corrections of order ${\cal O}(1/Q^2)$ whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi:2008ne}. In this paper, where we limit our
attention to effects of order ${\cal O}(1/Q)$, we can neglect $k^-$ compared to $q^-$. As a consequence, we can extend the integration over $dl^2$ to infinity, with the consequence that the jet correlator decouples from the parton correlator $\Phi$, and the inclusive structure functions only depend on the integrated jet correlator 
\begin{equation} 
  \Xi(l^-,{\bm l_T}) \equiv \int \frac{dl^2}{2l^-} \, \Xi(l) 
    =  \frac{\Lambda}{2 l^-}\,\xi_1 \id
    +  \xi_2 \frac{\nslash_-}{2} 
    + {\cal O}(l_T/l^-) + \text{higher\ twists} \ .
\end{equation} 
The neglected ${\bm l_T}$-dependent and higher twist terms only contribute to ${\cal O}(1/Q^2)$ to the inclusive cross section. Note that thanks to Eq.~\eqref{eq:jetfnsprops} we obtain
\begin{align}
\xi_1 &= \int d\mu^2 \frac{\mu}{\Lambda} J_1(\mu^2) 
       \equiv \frac{\mj}{\Lambda},
&
\xi_2 &= \int d\mu^2 J_2(\mu^2) = 1 \ ,
\end{align} 
where $\mj$ can be interpreted as the average invariant mass produced in the spin-flip fragmentation processes of a quark of flavor $q$.

It is important to notice that, while $\xi_2=1$ exactly due to CPT invariance
(see Sec.~10.7 of Ref.~\cite{Weinberg:1995mt}), the jet mass
$\mj < \int d\mu^2 \mu \, J_2(\mu^2)$ is dynamically determined. From the analytic properties of the spectral functions we expect that $J_2(\mu^2) = Z \delta(\mu^2-m_q^2) + \bar J_2(\mu^2) \theta (\mu^2-m_\pi^2)$, with $Z<1$ and the continuum starting at $m_\pi$ (the mass of the pion) due to color confinement effects, indicating $M_q=O(\Lambda_{QCD})$. However, in a dynamical confinement scenario, the spectral function $J_2$ needs not be positive definite \cite{Roberts:2016vyn} and we therefore estimate
$
  M_q\sim 10-100 \text{\ MeV}.
$
An experimental measurement of $M_q$ is anyway possible, as we discuss in Section~\ref{sec:moments}, and could shed some light on the confinement mechanism. We have also explicitly verified that $M_q>m_q$ in a model where quark fragmentation is simulated by a Yukawa pseudoscalar quark-meson interaction, already utilized, {\it e.g.}, in Ref.~\cite{Bacchetta:2001di}.

Although $\mj$ is in general a nonperturbative quantity, it is interesting to
notice that on the perturbative vacuum
\begin{align}
  \Xi^{\text{pert}}(l) = (\lslash + \mq \id) \, \delta(l^2-m_q^2) + {\cal O}(\alpha_s) \ ,
\end{align}
where $\mq$ is the current quark mass; therefore $\mj^\text{pert}=m_q$, and one recovers the result of the calculation with the conventional handbag diagram.
However, we are here considering nonperturbative effects
in the quark propagation, and $\mj \gg \mq$. 
Therefore, differently from $J_2$, the $J_1$ function leaves an imprint on the inclusive DIS cross section even in the asymptotic $Q^2 \to \infty$ regime.

@@

One should notice that since $h_1$ is slowly driven to 0 by QCD evolution as $Q^2 \to \infty$, the BC sum rule may still be satisfied at least asymptotically. At finite scales, however, the only way to preserve the validity of the BC sum rule is if
$
%\begin{align}
   \int dx\, \frac{1}{x} h_1^q(x) = 0 \ .
\label{eq:ABsumrule}
%\end{align}
$
Interestingly, one can show that this constraint, if valid at any given scale
$Q_0$, is conserved through QCD evolution. However, we think that it is unlikely to be satisfied in general, since the right hand side is different from zero
in perturbative QCD~\cite{Kundu:2001pk}, as well as in model calculations \cite{Schweitzer:2001sr,Wakamatsu:2007nc,Pasquini:2005dk,Cloet:2007em,Bacchetta:2008af,Bourrely:2010ng}.
A finite breaking of the BC sum rule would imply that $h_1(x)/x$ must be integrable, which is possible only if, at small $x$, the transversity goes as $h_1^q(x) \propto x^\epsilon$ with $\epsilon>0$. While $\epsilon=1$ in perturbative QCD \cite{Hayashigaki:1997dn,Vogelsang:1997ak}, the leading Regge contribution at small $x$ indicates that $\epsilon = 0$  \cite{Kirschner:1996jj}, and opens the door to a more drastic breaking of the sum rule.
Finally, we note that the small-$x$ behavior of the longitudinal spin structure function $g_1$ has been recently studied in Ref.~\cite{Kovchegov:2016zex}; however, since the small $x$ structure of the $h_1$ function may be quite different from that of $g_1$ \cite{Kirschner:1996jj},
it would be interesting to extend those techniques to the transverse spin structure functions $g_T=g_1+g_2$ and $h_1$, and investigate their role in the breaking of the BC sum rule.

@@

For both the $d_1$ and $d_2$ moments, the transversity contribution is a background to the extraction of the pure twist-3 piece. Fortunately, it is a quantity that can be extracted from the lattice
\cite{Green:2012ej,Bali:2014nma,Bhattacharya:2015wna,Abdel-Rehim:2015owa,Bhattacharya:2016zcn} 
or extracted form experimental data \cite{Radici:2015mwa,Anselmino:2015sxa,Kang:2015msa},
and information from the extended BC sum rule \eqref{eq:BC-sfn} promises to improve future transversity fits. Furthermore, as combined QCD fits of different distribution functions have now become possible \cite{Ethier:2017zbq}, the jet mass $M_q$ could also be considered as a free parameter in a combined helicity and transversity PDF fit. Therefore the pure twist-3 part can, in principle, be properly isolated and measured.

We should also note that the $\mj$ jet mass parameter can
be experimentally measured, \eg, in electron-positron collisions.
A promising avenue is through inclusive single hadron production, $e^+ e^- \to h X$, and inclusive dihadron 
production from the same hemisphere, $e^+ e^- \to h h X$, see~Fig.~\ref{fig:epl_emn_h}.
In single-hadron production, the fragmentation functions 
play the role of PDFs in DIS and couple to the jet functions
in an analogous way. To access the spin-flip $J_1$ function one needs to detect a polarized hadron, such as a $\Delta$ baryon. 
In double hadron production, the enlarged number of Dirac structures
of the dihadron fragmentation correlators related to the relative momentum of the two hadrons \cite{Bacchetta:2002ux,Bacchetta:2003vn} allows one to access
the jet function in novel ways, and in particular to isolate the
contribution from the helicity-flip $J_1$ term in combination with the
chiral-odd fragmentation function $H_1^{\sphericalangle}$.

@@

In this paper, we revisited the inclusive DIS analysis, including the
effects due to the production of a system of final state hadrons in the current direction, which we
conveniently referred to as a ``jet.'' We described this in terms of a jet
correlator that corresponds, up to twist-4 contributions, to the nonperturbative quark cut propagator, or, equivalently, to the quark's spectral function, and of a quark-gluon-quark jet correlator needed to insure gauge invariance of the calculation.
We then carried out the analysis of
the DIS cross section up to contribution of order $1/Q$. 
The introduction of the jet correlators 
leads to a difference in the expression of the structure function $g_2$ in
inclusive DIS with respect to the standard analysis: a new term appears, proportional to a jet mass parameter $\mj={\cal O}$(10-100 MeV)
and to the transversity distribution function. This new term
contributes to the violation of the Wandzura-Wilczek relation, in addition to
the standard pure twist-3 terms and quark mass corrections. Contrary to these
standard terms, however, the new jet mass correction does not necessarily integrate to zero and so violates also the
Burkhardt--Cottingham and Efremov--Teryaev--Leader sum rules. This is yet another example of how surprising
and rich the phenomenology of polarized inclusive DIS can be,
and offers a new direction for theoretical studies and experimental investigations of spin physics over a wide range in $x$, from the valence and sea regions at Jefferson Lab \cite{Dudek:2012vr} to the small-$x$ region at the future Electron-Ion Collider \cite{Accardi:2012qut}.
